### 2010-06-24 resume_cv/cv.tex
Updated my cv and my list of applications

\section{Education}
%
{\textbf{Brigham Young University}},
Provo, Utah USA
\begin{outerlist}
\item[] B.S.,
		Computer Science, April 2010
        \begin{innerlist}
        \item Minors in Physics and Mathematics
        \item Graduated with a 4.0 GPA and University honors (anticipated)
        \item Thesis Topic: \emph{Speculative Evaluation in Particle Swarm
            Optimization}
        \item Advisor: Professor Kevin Seppi
        \end{innerlist}

@@

\section{Academic Experience}
{\textbf{Brigham Young University}},
Provo, Utah USA
\begin{outerlist}

\item[] \textit{Undergraduate Researcher}%
        \hfill \textbf{December 2007 to Present}
\begin{innerlist}
\item Worked in the Applied Machine Learning Lab in the Computer Science
  Department under Dr. Kevin Seppi.
\item Reviewed papers for the International Conference on Machine Learning 2009.
\item Research topics included particle swarm optimization and Markov decision
  processes.
\end{innerlist}
\end{outerlist}

>>>>

\section{Education}
%
{\textbf{Brigham Young University}},
Provo, Utah USA
\begin{outerlist}
\item[] B.S.,
		Computer Science, April 2010
        \begin{innerlist}
        \item Minors in Physics and Mathematics
        \item Graduated summa cum laude (GPA 4.0) and with University honors
        \item Thesis Topic: \emph{Speculative Evaluation in Particle Swarm
            Optimization}
        \item Advisor: Professor Kevin Seppi
        \end{innerlist}

@@

\section{Academic Experience}
{\textbf{Johns Hopkins University}}, Baltimore, Maryland USA
\begin{outerlist}

\item[] \textit{Human Language Technologies Summer School Attendee}%
        \hfill \textbf{June 2010}
\begin{innerlist}
\item One of seven recipients of a NAACL scholarship to attend the summer school
  at JHU.
\item Studied with top researchers in HLT at JHU and the University of Maryland.
\end{innerlist}
\end{outerlist}

\blankline

{\textbf{Brigham Young University}}, Provo, Utah USA
\begin{outerlist}
\item[] \textit{Teaching Assistant}%
	\hfill \textbf{May 2010 to June 2010}
\begin{innerlist}
\item CS 470: Introduction to Artificial Intelligence.  Tutored students,
  graded homework and reports, and helped create new curriculum for the class.
\item CS 677: Bayesian Inference.  Tutored students and graded homework and
  reports.
\end{innerlist}

\item[] \textit{Undergraduate Researcher}%
        \hfill \textbf{December 2007 to April 2010}
\begin{innerlist}
\item Worked in the Applied Machine Learning Lab in the Computer Science
  Department under Dr. Kevin Seppi.
\item Reviewed papers for the International Conference on Machine Learning 2009.
\item Research topics included particle swarm optimization and Markov decision
  processes.
\end{innerlist}
\end{outerlist}
